---
title: "Defining Sequences in R"
subtitle: "CIS 351:"
date: today
author: ""
format:
  html:
    embed-resources: true
    code-overflow: wrap
    number-sections: true
---

## Load Packages and Data

```{r}
#| message: false
library()

library()

library()

library()

dogs <- read_csv() |>
  clean_names()

earthquakes <- read_csv() |>
  clean_names()

fastfood <- read_csv() |>
  clean_names()
```

## Defining Integer Sequences

### The `:` operator 

The symbol `:` allows us to quickly create a vector of consecutive integers in R. This opeator is often called the **sequence operator**. 

:::{.callout-note icon='false'}
## Example 1.

a. Create a vector of numerical values from 1 to 100.
b. Create a vector of numerical values from 100 to 450.

```{r}
# (a)

```

```{r}
# (b)

```
:::

### The `seq()` function

The `seq()` function in R generates sequences of numbers according to specified starting values, ending values, increments, or lengths. It provides greater flexibility than the `:` operator because it can create sequences with custom step sizes and a specified number of values.

:::{.callout-note icon='false'}
## Example 2.

Use the `seq()` function to generate a vector of numberic values that range from 1 to 100.

_Solution._

```{r}

```
:::

:::{.callout-note icon='false'}
## Example 3.

Use the `seq()` function to generate a vector of numeric values that range from 100 to 450.

_Solution._

```{r}

```
:::

:::{.callout-note icon='false'}
## Example 4.

Use the `seq()` function to generate a vector of numeric values that range form 1 to 20, incrementing by 4.

```{r}

```
:::

:::{.callout-note icon='false'}
## Example 5.

Use the `seq()` function to generate a vector of numeric values that range from 4 to 28, where the length of the vector is 6.

_Solution._

```{r}

```
:::