---
title: "Factors"
subtitle: "CIS 351:"
date: ""
author: ""
format:
  html:
    embed-resources: true
    code-overflow: wrap
    number-sections: true
---

## Load Packages and Data

```{r}
#| message: false
library()

library()

library()

library()

dogs <- read_csv() |>
  clean_names()

earthquakes <- read_csv() |>
  clean_names()

fastfood <- read_csv() |>
  clean_names()
```

## Factors

Recall from elementary statistics that numerical variables have an inherent order, whereas categorical variables do not. However, it is sometimes necessary to have an ordered categorical variable. In R, **factors** are used to represent such ordered categorical variables.

:::{.callout-note icon='false'}
## Example 1.

Apply the `sort()` function to `weekdays` vector defined below. What is the resulting output in R?

```{r}
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
```

_Solution._
```{r}

```
:::

To convert a categorical variable into a factor, we use the `factor()` function. By specifying the optional `levels` argument, we can define the order of the categories in the resulting factor.

:::{.callout-note icon='false'}
## Example 2.

Convert the `weekdays` vector into a ordered factor with Sunday as the first day of the week and Saturday as the last day of the week.

_Solution._

```{r}

```
:::