---
title: "Import Data into Positron"
subtitle: "CIS 351:"
date: ""
author: "Your Name"
format: 
  html:
    embed-resources: true
---

## Learning Objectives

* Import `.csv` and `.xlsx` files into Positron
* Assign variable names to imported data
* Use the `names()` and `head()` functions to preview data

```{r}
#| message: false

library()

library()

library()
```

## Preparatory Work

First, make sure that the file is in the current working folder. In this lesson, our current working folder is **Week 2**. 

## Importing CSVs

We use the `read_csv()` function to import a `.csv` file into the Quarto document.

:::{.callout-note icon='false'}
## Example 1.

Import the `dogs.csv` into the Quarto document and name it `dogs`.

```{r}

```
:::

:::{.callout-important}
Make sure that the directory names are separated by the forward slash symbol (`/`) and not the backslash symbol (`\`). In Windows, Positron is known to use the incorrect slash symbol when copying file paths.
:::

:::{.callout-note icon='false'}
## Example 2.

Import the `fastfood.csv` into the Quarto document and name is `fastfood`. Use the `names()` function to display the column names of `fastfood` and the `head()` function to show the first six rows of the data.

```{r}

```
:::

## Importing Excel Workbooks

We use the `excel_sheets()` function to list all sheet names of an Excel Workbook and the `read_excel()` function to import an Excel Workbook (or worksheet) into the Quarto document.

:::{.callout-note icon='false'}
## Example 3.

Print the sheet names of `week_2_day_1_excel_counting_1.xlsx` and import the `dogs` sheet into the Quarto doc.

```{r}

```

```{r}

```
:::